NLIZE: a Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-23 paper/intro.tex
minor correction to intro

We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as neural machine translation, and text summarization, etc.
%
In the simplest form, the inference task ask the question about whether if we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or are they contradict with each other (\emph{contradiction}), or are they talk about different/unrelated things (\emph{neutral}). Language inference addresses the fundamental challenge of measuring sentences' semantic similarity, and is one the core natural language processing tasks (see detail in Section~\ref{sec:languageInference}).

One recent advance in neural natural language process models is the introduction of attention mechanisms~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}). Intuitively, the \emph{attention} help capture which part of the input the model deemed more important for making the right prediction. The attention is often represented as weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
%
%\shusen{seems repeated some of the previous points}
There have been many speculations on how attention works in various models. By utilizing the proposed tool, the domain experts study how changes in sentence input, attention, or prediction affect each other, which help them develop deeper intuitive and alternative hypotheses. 
%we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention. And more importantly, we also allow the user to change prediction, where we apply a constrained optimization to find the least amount of parameter update to produce the user assign label. 
%Another word, 
%Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
Moreover, we enhanced the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual representation.
%
Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate the potential benefit of including the linguistic structure in the design of attention component of the model.

>>>>

We implement our vision of the perturbation-driven exploration in an interactive visualization system for natural language inference models~\cite{Parikh2016}.
However, the components of the visualization and the overall paradigm can be readily extended to other NLP tasks, such as question and answer, and text summarization, etc.
%
In the simplest form, the inference task asks the question about whether if we can infer the content of \textbf{sentence B} from \textbf{sentence A} (\emph{entail}), or are they contradict with each other (\emph{contradiction}), or are they talk about different/unrelated things (\emph{neutral}). Language inference addresses the fundamental challenge of measuring sentences' semantic similarity, and is one the core NLP tasks (see detail in Section~\ref{sec:languageInference}).

One recent advance in neural natural language process models is the introduction of \emph{attention mechanisms}~\cite{VaswaniShazeerParmar2017} (Section~\ref{sec:attention}). Intuitively, the attention helps capture which part of the input the model deemed more important for making a prediction. The attention is often represented as weights for individual words or pairs of words (i.e., the alignment between words in different sentences).
%
%\shusen{seems repeated some of the previous points}
There have been many speculations on how attention works in various models. By utilizing the proposed tool, the domain experts study how changes in sentence input, attention, or prediction affect each other, which help them develop deeper intuitive and alternative hypotheses. 
%we can perturb the attention and observer the change in the prediction, perturb the sentence input and observe the effects on the attention. And more importantly, we also allow the user to change prediction, where we apply a constrained optimization to find the least amount of parameter update to produce the user assign label. 
%Another word, 
%Such type of exploration is not only essential to interpret the language inference problem, but can also be generalized to other NLP model utilized the attention mechanisms.
Moreover, we enhanced the standard visual encoding (e.g., as a bipartite graph or as a matrix) of the attention matrix by overlaying sentence linguistic structure to allow grammar guided simplification of the visual representation.
%
Finally, as discussed in Section~\ref{sec:caseStudy}, the ability to examine how attention corresponds to the grammatical structure also enables domain experts to speculate the potential benefit of including the linguistic structure in the design of attention component of the model.
